Appendix for: "Bad Forecast, Good Decision

### 2021-03-30 manuscript/appendix_B.Rmd
tidy up
tweak

knitr::opts_chunk$set(cache=FALSE, tidy = "styler", message = FALSE, warning = FALSE, echo = FALSE)

@@

# max is at 4 * K / 5 
f3  <- function(x, h = 0, r = .002, K = 10){
  s <- pmax(x - h, 0)
  s + s ^ 4 * r * (1 - s / K)
}
```

```{r}
rs <- c(0.01, 0.1, 0.2, 0.3, 0.4, 0.5, 2)
Ks <- c(0.5, 1, 1.5, 4, 10, 16)
n_models <- length(rs)*length(Ks)
sigmas <- 0.1
pars <- expand.grid(rs, Ks)
names(pars) <- c("r", "K")
pars$sigma <- sigmas

@@

@@

@@

```{r plot_models, fig.width=6, fig.height=4}
model_set <- models
names(model_set) <- c("true", 1:n_models)
d <- 
  map_dfc(model_set, function(f) f(states) - states) %>%
  mutate(state = states)

d %>% pivot_longer(names(model_set[-1]), "model") %>%
  mutate(model = as.numeric(model)) %>%
  ggplot(aes(state, value, col = model)) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_point(alpha = .5) + 
  geom_line(aes(state, true), col = "red") +
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x") + viridis::scale_color_viridis()

@@

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))
x0 <- which.min(abs(states - 6))
## start with 90% weight on 'model 1'
model_prior <- c(rep(.1, length(models)-2) / (length(models) - 2), .9)

am_many <- adaptive_management(transitions[-1],  
                           reward = reward, 
                           discount = discount,
                           model_prior = model_prior,
                           x0 = x0, 
                           Tmax = 20, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

```{r}
posteriors <- data.frame(r = rs, K = Ks, t(am_many$posterior)) %>%
  pivot_longer(starts_with("X"), 
               values_to = "probability",
               names_to = "time") %>% 
  mutate(time = as.integer(as.factor(time)))

i <- 10:20
r_marginals <- posteriors %>% group_by(time,r) %>% 
  summarise(prob = sum(probability), .groups = "drop") %>% 
  filter(time %in% i)

r_marginals %>%  ggplot(aes(r, prob, group=time)) + geom_line() + facet_wrap(~time)
```

## Marginal Posterior Probability evolution over K

```{r}
i = 19
K_marginals <- posteriors %>% group_by(time,K) %>% 
  summarise(prob = sum(probability), .groups = "drop") %>% 
  filter(time %in% i) 
K_marginals %>%
  ggplot(aes(K, prob, group=time)) + geom_path() + geom_point() + facet_wrap(~time)

```{r}
Tmax <- max(am_many$df$time)
best_i <- which.max(am_many$posterior[Tmax,])
good_i <- am_many$posterior[Tmax,] > 0.1
pars[good_i,] %>% mutate(final_prob = as.numeric(am_many$posterior[Tmax,good_i])) %>% knitr::kable("latex")
```

```{r, fig.cap = ""}
model1 <- dim(am_many$posterior)[2]
am_many$df %>% 
  mutate(belief = am_many$posterior[,model1]) %>%
  ggplot(aes(time, states[state], col = belief)) + 
  geom_line() + 
  geom_point() +
  scale_colour_gradient(limits = c(0,1), low = pal[4], high = pal[1]) + 
  ylab("fish stock") + labs(caption = "Belief in model 1 falls off rapidly as magagement pushes stocks to lower and lower sizes.")

```{r}
am_npv <- sum(am_many$df$value * discount ^ am_many$df$time)
am_npv
```

>>>>

knitr::opts_chunk$set(cache=FALSE, tidy = "styler", message = FALSE, warning = FALSE, echo = TRUE)

@@

# max is at 4 * K / 5 
f3  <- function(x, h = 0, r = .002, K = 10){
  s <- pmax(x - h, 0)
  s + s ^ 4 * r * (1 - s / K)
}

n_models <- 30
rs <- seq(0.05, 2, length.out = n_models)
Ks <- seq(0.1, 10*8/5, length.out = n_models)
sigmas <- seq(0.05, 1.5*0.05, length.out = n_models)
pars <- data.frame(r = rs, K = Ks, sigma = sigmas)

@@

This follows the standard setup for standard stochastic dynamic programming, see @Marescot2013. Having defined a function to compute the transition matrix, we can use it to create matrices corresponding to each of the three models:

@@

Likewise, a corresponding matrix defining the rewards associated with each state $X$ and each harvest action $H$ can also be defined.

@@

```{r plot_models}
model_set <- models
names(model_set) <- c("true", as.character(round(Ks, 2)))
d <- 
  map_dfc(model_set, function(f) f(states) - states) %>%
  mutate(state = states)

d  %>%
  pivot_longer(names(model_set[-1]), "model") %>%
  mutate(model = as.numeric(model)) %>%
  ggplot(aes(state, value, col = model, group=model)) +
  geom_hline(aes(yintercept = 0), lwd=1) + 
  geom_line(alpha = .8) + 
  geom_line(aes(state, true), col = "red") +
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16)) +
  ylab(bquote(f(x) - x)) + xlab("x") + viridis::scale_color_viridis()
```

@@

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))
x0 <- which.min(abs(states - 6))

am_many <- adaptive_management(transitions[-1], 
                           reward, 
                           discount, 
                           x0 = x0, 
                           Tmax = 25, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

```{r}
i <- 1:20
posteriors <- data.frame(r = rs, K = Ks, t(am_many$posterior[i,])) %>%
  pivot_longer(starts_with("X"), 
               values_to = "probability",
               names_to = "time") %>% 
  mutate(time = as.integer(as.factor(time))) %>%
  pivot_longer(c("r", "K"), names_to="parameter")

posteriors %>%
  ggplot(aes(value, probability, group=time, col=time)) +
  geom_line(show.legend = FALSE) +
  facet_grid(~parameter, scales="free")
```

```{r}
best_model <- which.max(am_many$posterior[20,])
```

```{r, fig.cap = ""}
am_many$df %>% 
  mutate(belief = am_many$posterior[,best_model]) %>%
  ggplot(aes(time, states[state], col = belief)) + 
  geom_line() + 
  geom_point() +
  scale_colour_gradient(limits = c(0,1), low = pal[1], high = pal[4]) + 
  xlab("fish stock")
```

```{r}
am_npv <- sum(am_many$value * discount ^ am$time)
am_npv / npv[[1,"npv"]]
```

```{r include = FALSE}
as_tibble(am1$posterior) %>% 
  mutate(time = seq_along(V1)) %>%
  select(time = time, "1" = V1, "2" = V2) %>% 
  pivot_longer(c("1", "2"), values_to="belief", names_to = "model") %>%
  ggplot(aes(time, belief, col=model)) + geom_line(col = pal[4])
```
